---
engine: knitr
---

# 測試

```{r}
plot(pressure)
```

## Test 

```{python}
#| results: asis
#| echo: false
import lipsum

lipsum.generate_words(266)
```


## Test 

```{python}
#| results: asis
#| echo: false
import lipsum

lipsum.generate_words(266)
```

## Test 

```{python}
#| results: asis
#| echo: false
import lipsum

lipsum.generate_words(266)
```



# Blocks

## Equations

Here is an equation.

\begin{equation} 
  f\left(k\right) = \binom{n}{k} p^k\left(1-p\right)^{n-k}
  (\#eq:binom)
\end{equation} 

You may refer to using `\@ref(eq:binom)`, like see Equation \@ref(eq:binom).


## Theorems and proofs

Labeled theorems can be referenced in text using `\@ref(thm:tri)`, for example, check out this smart theorem \@ref(thm:tri).

::: {.theorem #tri}
For a right triangle, if $c$ denotes the *length* of the hypotenuse
and $a$ and $b$ denote the lengths of the **other** two sides, we have
$$a^2 + b^2 = c^2$$
:::

Read more here <https://bookdown.org/yihui/bookdown/markdown-extensions-by-bookdown.html>.

## Callout blocks


The `bs4_book` theme also includes special callout blocks, like this `.rmdnote`.

::: {.rmdnote}
You can use **markdown** inside a block.

```{r collapse=TRUE}
head(beaver1, n = 5)
```

:::

It is up to the user to define the appearance of these blocks for LaTeX output. 

You may also use: `.rmdcaution`, `.rmdimportant`, `.rmdtip`, or `.rmdwarning` as the block name.


The R Markdown Cookbook provides more help on how to use custom blocks to design your own callouts: https://bookdown.org/yihui/rmarkdown-cookbook/custom-blocks.html



# Footnotes and citations 

## Footnotes

Footnotes are put inside the square brackets after a caret `^[]`. Like this one ^[This is a footnote.]. 

## Citations

Reference items in your bibliography file(s) using `@key`.

For example, we are using the **bookdown** package [@R-bookdown] (check out the last code chunk in index.Rmd to see how this citation key was added) in this sample book, which was built on top of R Markdown and **knitr** [@R-knitr] (this citation was added manually in an external file book.bib). 
Note that the `.bib` files need to be listed in the index.Rmd with the YAML `bibliography` key.

@R-bookdown

@R-knitr


The `bs4_book` theme makes footnotes appear inline when you click on them. In this example book, we added `csl: chicago-fullnote-bibliography.csl` to the `index.Rmd` YAML, and include the `.csl` file. To download a new style, we recommend: https://www.zotero.org/styles/


The RStudio Visual Markdown Editor can also make it easier to insert citations: <https://rstudio.github.io/visual-markdown-editing/#/citations>


TTTTTTTTTTTTTTTTTTTTTTTTTTTTTTTTTTTTTTTTT

BBBBBBBBBBBBBBBBBBBBBBBBBBBBBBBBBBBBBBBBBBBB

CCCCCCCCCCCCCCCCCCCCCCCCCCCCC


DDDDDDDDDDDDDDDDDDDDDDDDDDDDDDDDDDDD

EEEEEEEEEEEEEEEEEEEEEEEEEEEEEEE